DMRGenie: Graphical interface for entanglement renormalization

### 2024-12-30 paper/paper.tex
Update paper.tex

A.D.~acknowledges support from the Undergraduate Student Research Award (USRA) from NSERC

@@

K.G. and A.D.~acknowledge the Jamie Cassel's Undergraduate Research Award (JCURA).

@@

This research was enabled--in part--by support and resources provided by the Research Support Services at the University of Victoria.

>>>>

@@

A.D.~acknowledge the Jamie Cassel's Undergraduate Research Award (JCURA). A.D.~acknowledges support from the Undergraduate Student Research Award (USRA) from NSERC.

@@

This research was enabled in part by support and resources provided by the Research Support Services at the University of Victoria.
